|

### 2021-06-14 01-Chp-Background.Rmd
End of day: -2951

This chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each. It briefly discusses the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention research. It then provides background on blood lipids and lipid-modifying treatments, and summarises the existing evidence on the effect of these exposures on dementia outcomes.

@@

Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases. Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can either onset quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]

The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g. Parkinson's disease).[@burns2009]

@@

Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expect progression and potential treatment options available (see Section \@ref(intro-treatments)). Cause-specific criteria exist for the diagnosis of dementia sub-types. For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]

@@

Dementia is quickly becoming a critically important public health issue. Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only once without a proven treatment.

@@

<!--- May need small bit here on converting from one measurement to the other i.e.
mg/dL to mmol/L--->

@@

Triglycerides are the simplest and most common type of lipids found across the body. They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities. Low-Density-Lipoprotein-cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor. In contrast, High Density-Lipoprotein-cholestel (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]

@@

Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels. These deposits constrict blood flow and can lead to vascular complications. Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organisation to be approximately 40%.

@@

Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA Reductase (HMG-CoA-R). This conversion limits the rate at which cholesterol can be produced, enabling statins to effectively reduce the production of LDL cholesterol.

@@

```{r eval = FALSE, statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
```

@@

There are a range of other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)). However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.

@@

A second example are fibrates, used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver. They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.

@@

Multiples forms of evidenc

@@

The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base. The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered, or to provide an additional source of evidence for an existing question.

This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
Specifically, this thesis considers three methodologies within the umbrella term of evidence synthesis:

* Inclusion of grey literature
* Triangulation across evidence sources
* Individual patient data meta-analysis

@@

### Inclusion of grey literature {#diverse-sources-preprints}

@@

As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk. However, each method is limited by its own unique biases. Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about a exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result. The ideal scenario is where predicted sources of bias are likely to be in competing directions, one expected to increased the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias. A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.

@@

In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not presenting results stratified by covariates of interests, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]

An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all dataset, potentially eliminating some important sources of heterogeneity.[@stewart2002]

Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies is frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a]. Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]

@@

This thesis will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading). Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
<!----------------------------------------------------------------------------->

@@

### Hypothesis

Circulating blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, affect the subsequent risk of dementia and related outcomes.

@@

>>>>

This chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each. It briefly discusses the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention research. It then provides background on blood lipids and lipid-modifying treatments, and summarises the types of evidence used to examine the effect of these exposures on dementia outcomes.

@@

Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases. Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]

The remaining 10-30% of cases are caused by other dementia subtypes (e.g. Lewy body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g. Parkinson's disease).[@burns2009]

@@

Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expected progression and potential treatment options available (see Section \@ref(intro-treatments)). Cause-specific criteria exist for the diagnosis of dementia sub-types. For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]

@@

Dementia is quickly becoming a critically important public health issue. Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only one without a proven cure.

@@

@@

Triglycerides are the simplest and most common type of lipids found across the body. They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities. Low-density-lipoprotein cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor. In contrast, High density-lipoprotein cholesterol (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]

@@

Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels. These deposits constrict blood flow and can lead to vascular complications. Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organization to be approximately 40%.

@@

<!-- TODO Need more on this: maybe a diagram of the pathway -->

<!-- REVIEW [JH] This section seems very short for such a key entity in your thesis. I don’t know exactly what else there is to say about statins, but I recommend expanding it a bit, The second sentence is gobbledygook to me. -->

Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA reductase (HMG-CoA-R). This conversion limits the rate at which cholesterol can be produced, enabling statins to reduce effectively the production of LDL cholesterol.

@@

```{r statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
knitr::include_graphics(file.path("figures/background/statinPath.png"))
```

@@

There are several other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)). However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.

@@

Fibrates provide a second example of non-statin therapy. They are used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver. They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.

@@

@@

The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base. The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered.

This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
Specifically, this thesis considers three concepts within the umbrella term of evidence synthesis:

* Inclusion of preprints
* Triangulation across evidence sources
* Individual patient data meta-analysis

@@

### Inclusion of preprints  {#diverse-sources-preprints}

<!-- TODO Incorporate Julian's comments below -->

<!-- REVIEW [JH] I think, on general reflection, that portraying this as an issue around “grey literature” may not be particularly useful. Preprints are arguably some of the least “grey” of the very ambiguously defined family of grey sources, such that some definitions of “grey” might not include them.
It seems to me that preprints are such a big and important part of the landscape now that you can just portray the methodology as dealing with preprints rather than including grey literature.
Interesting debate as to whether preprints are grey literature, given that many of them are increasingly becoming findable in electronic bibliographic databases. We have no clear and widely used definition of grey literature.  -->

@@

As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk. However, each method is limited by its own biases. Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result. The ideal scenario is where predicted sources of bias are likely to be in competing directions, strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias. A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.[@munafo2018]

@@

In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]

An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all datasets, potentially eliminating some important sources of heterogeneity.[@stewart2002]

Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a]. Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]

@@

I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading). Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
<!----------------------------------------------------------------------------->

@@

@@

The over-arching aim of this thesis is to explore the relationship between blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, and the subsequent risk of dementia and related outcomes

### 2021-06-14 03-Chp-Systematic-Review.Rmd
End of day: -2951

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does. [@cohen1960: @gwet2008; @wongpakaran2013]

Gwet's AC1 is defined as

@@

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

@@

As part of the IPD analysis, relevant cohort studies were identified and approached. In the first instance, the corresponding author on the main man

@@

@@

@@

<!-- # ```{r agreementtableinter, echo = FALSE} -->

<!-- # ``` -->

<!-- # ```{r agreementtableintra, echo = FALSE} -->

<!-- # ``` -->

For the inter-rater reliability, percentage agreement was 97.3% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)), while for the intra-rater reliability, agreement was 98.6% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)).

The discrepancy between the percent agreement and the associated value of AC is expected, due to the heavy imbalance in this sample towards exclusion.[@feinstein1990]

Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated. This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.

@@

### Added evidental value of including preprints {}

@@

>>>>

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review, this is an important characteristic.

Gwet's AC1 is defined as:

@@

How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement. Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

@@

Where data points required either for the analysis or risk-of-bias assessment but were not reported, the primary authors of the study were contacted. This approach was taken due to the potentially large impact of following up with authors on the results of the review,[@reynders2019]

This was particular important for the dose response meta-analysis, we

@@

<!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->

@@

When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the widht of the higest category was the same as the one immediately below it. Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).

we assumed the width of the category to be the same as the adjacent category.
When the lowest category was open ended, we set the lower boundary to zero.

@@

<!----------------------------------------------------------------------------->
(ref:agreeInter-caption) Inter-rater agreement on a subset of ~10% of records, illustrating high accuracy.

<!-- TODO Include AC1 result in caption above -->

(ref:agreeInter-scaption) Inter-rater agreement

```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.

(ref:agreeIntra-scaption) Inter-rater agreement

```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

For the inter-rater reliability, agreement was very high ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)). Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeIntra-table)). The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]

Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`) were investigated. This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.

Additionally, records I excluded on my second viewing (n=`r discrepancy_Intra`) were investigated. All were . . .

@@

### Added evidental value of including preprints {sys-rev-including-preprints}

@@

<!-- TODO This section will be informed by the review published as a preprint -->

### 2021-06-14 05-Chp-IPD-Analysis.Rmd
End of day: -2951

@@

@@

## Risk of bias assessment

@@

## Data cleaning

@@

Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responsed if at all. Will also need to comment on the additional tactics used.

@@

>>>>

## Lay Summary

## Introduction

@@

As part of the IPD analysis, relevant cohort studies were identified from the sty and approached. In the first instance, the corresponding author on the main man

@@

Several DPUK cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).

See

### Risk of bias assessment

@@

### Data cleaning

@@

Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responded if at all. Will also need to comment on the additional tactics used.

@@

### Study within a review

In future, it could have been worth running a "study within a review", such as that used to examine whe

https://bmjopen.bmj.com/content/9/1/e025273

### 2021-06-14 index.Rmd
End of day: -2951

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy in Population Health Sciences
degreedate: TBC
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

>>>>

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy in Population Health Sciences
degreedate: TBC
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
covidStatment: |
  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations
